Examining the critical path neighborhood for flexible job shop problems

### 2016-01-25 paper/paper.tex

\documentclass[a4paper,10pt]{article}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{booktabs}

@@

\begin{abstract}

This is my abstract.

\end{abstract}

@@

\subsubsection{Infeasible solutions}

@@

\begin{figure}[h]
\centering
\begin{ganttchart}[
		x unit=0.7cm,
		y unit chart=0.7cm,
		canvas/.style={draw=none, fill=none},
		vgrid,
		vgrid={*1{draw=black!12}},
		inline,
		group/.style={draw=none, fill=none},
		bar top shift=0.1,
		bar height=0.8,
		y unit title=0.5cm,
		title/.style={draw=none, fill=none},
		%title label/.style={align=left},
		include title in canvas=false,
	]{655}{669}

@@

The rest of the instances were generated using a random instance generator built for this purpose. These are labeled \emph{v10 -- v43}. The optimal makespans for these instances is unknown. However, they do provide insight into the convergence behavior, especially when compared between instances.

The local search was implemented in C, using the GCC compiler with the -O3 flag. The times listed are for an Intel Core i3 M370 @ 2.40 Hz. These results can be examined in \textbf{Table \ref{table:fjs}}.

\begin{table}[h]
\centering
\small
\begin{tabular}{@{\bfseries}rrrrrrrrrrrr}
	\toprule
	\multicolumn{4}{c}{Instance} & \multicolumn{2}{c}{Properties} && \multicolumn{5}{c}{Results} \\
	\cmidrule(r){1-4} \cmidrule(lr){5-6} \cmidrule(lr){8-12}
	\normalfont{name} & $|\mathcal{J}|$ & $|\mathcal{T}|$ & $|\mathcal{M}|$ & $\max C_\text{job}$ &
	$C_\text{opt}$ && $\alpha$ & restarts & $\bar{C}$ & $C_\text{best}$ & $\bar{t}$ \\
	\midrule
	ft06 &  6 &  6 &  6 &   47 &   55 &&    0.9 & 1 &   55 &   55 &    0 \\
	ft10 & 10 & 10 & 10 &  655 &  930 &&    0.9 & 5 &  954 &  941 &    2 \\
	     &    &    &    &      &      &&   0.99 & 5 &  943 &  938 &   18 \\
	     &    &    &    &      &      &&  0.999 & 5 &  933 &  930 &  182 \\
	ft20 & 20 &  5 &  5 &  387 & 1165 &&    0.9 & 5 & 1215 & 1186 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 & 1182 & 1178 &   13 \\
	     &    &    &    &      &      &&  0.999 & 5 & 1170 & 1165 &  130 \\[2ex]
	c1   &  4 &  2 &  4 &   34 &   34 &&    0.9 & 1 &   34 &   34 &    0 \\
	c2   &  4 &  2 &  4 &   53 &   53 &&    0.9 & 1 &   53 &   53 &    0 \\
	c3   &  4 &  2 &  4 &  133 &  143 &&    0.9 & 1 &  143 &  143 &    0 \\
	c4   &  6 &  2 &  4 &   52 &   57 &&   0.99 & 5 &   57 &   57 &    2 \\
	c5   &  6 &  2 &  4 &  105 &  113 &&   0.99 & 5 &  113 &  113 &    2 \\
	c6   &  6 &  2 &  4 &  205 &  225 &&   0.99 & 5 &  225 &  225 &    2 \\
	c7   &  4 &  3 &  9 &   39 &   39 &&    0.9 & 1 &   39 &   39 &    0 \\
	c8   &  4 &  3 &  9 &   64 &   64 &&    0.9 & 1 &   64 &   64 &    0 \\
	c9   &  4 &  3 &  9 &  138 &  138 &&    0.9 & 1 &  138 &  138 &    0 \\
	c10  &  6 &  3 &  9 &   50 &   50 &&    0.9 & 1 &   50 &   50 &    0 \\
	c11  &  6 &  3 &  9 &  103 &  103 &&    0.9 & 1 &  103 &  103 &    0 \\
	c12  &  6 &  3 &  9 &  204 &  204 &&    0.9 & 1 &  204 &  204 &    0 \\
	c13  &  8 &  3 &  9 &  337 &  337 &&    0.9 & 5 &  337 &  337 &    0 \\
	c14  &  8 &  3 &  9 &  705 &  705 &&    0.9 & 5 &  705 &  705 &    0 \\
	c15  &  8 &  3 &  9 & 1458 & 1458 &&    0.9 & 5 & 1458 & 1458 &    0 \\
	c16  & 10 &  4 & 16 &  405 &  405 &&    0.9 & 5 &  405 &  405 &    0 \\
	c17  & 10 &  4 & 16 &  955 &  955 &&    0.9 & 5 &  955 &  955 &    0 \\
	c18  & 10 &  4 & 16 & 1621 & 1621 &&    0.9 & 5 & 1621 & 1621 &    0 \\
	c19  & 15 &  5 & 25 & 2631 & 2631 &&    0.9 & 5 & 2631 & 2631 &    0 \\[2ex]
	v20  &  8 &  2 &  4 &      &      &&    0.9 & 5 &      &      &      \\
	v30  & 16 &  2 &  4 &  666 &      &&    0.9 & 5 & 2382 & 2381 &   10 \\
	     &    &    &    &      &      &&   0.99 & 5 & 2381 & 2381 &  102 \\
	v31  & 16 &  2 &  8 &  566 &      &&    0.9 & 5 &  963 &  961 &   12 \\
	     &    &    &    &      &      &&   0.99 & 5 &  960 &  959 &  126 \\
	v32  & 16 &  4 &  8 &  655 &      &&    0.9 & 5 & 1119 & 1116 &   11 \\
	     &    &    &    &      &      &&   0.99 & 5 & 1112 & 1111 &  116 \\
	\bottomrule
\end{tabular}
\caption{Computational results for the FJS}
\label{table:fjs}
\end{table}

Most of the parameters in the table are self-explanatory. $\alpha$ is the cooling parameter. It is responsible for lowering the tempterature of the simulated annealing process. A value closer to 1 means the temperature cools slower, and thus the heuristic searches longer. The restarts column indicates how many times the temperature was reset. This entire process was repeated five times for every instance, to provide an average best solution found ($\bar{C}$) and the average running time ($\bar{t}$).

@@

For the Job Shop instances (\emph{ft06}, \emph{ft10}, and \emph{ft20}), the code as well as previous results in literature \cite{simulatedannealingjsp}. This gives us confidence that the code is robust.

The series of instances from the previous project (\emph{c1 -- c19}) are largely uninteresting, due to there being too few jobs in relation to machines. Interestingly, the few instances whose optimal makespans were larger than the lower bound given by the job makespans gave the search more trouble, despite being much smaller than some of the other instances. In several cases, the search failed to find an optimal solution despite the restarts, being very slightly off. However, this was averaged out by the other results. It should be noted that there were several instances of the algorithm becoming stuck, with the only neighborhood solution available being infeasible. This is very rare, but it highlights the importance of random restarts, when using the critical path neighborhood for the FJS.

@@

@@

The same instances are used as before. A new column, containing the best non-blocking solution for the instance, is added for comparison.

\begin{table}[h]
\centering
\small
\begin{tabular}{@{\bfseries}rrrrrrrrrrrrr}
	\toprule
	& FJS & FBJS & && \multicolumn{2}{c}{Critical Path} &&
	\multicolumn{2}{c}{Naive shift} && \multicolumn{2}{c}{Both} \\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){6-7}
	\cmidrule(lr){9-10} \cmidrule(lr){12-13}
	\normalfont{name} & $C_\text{best}$ & $C_\text{opt}$ & $\alpha$ && $\bar{C}$ & $C_\text{best}$ &&
	$\bar{C}$ & $C_\text{best}$ && $\bar{C}$ & $C_\text{best}$ \\
	\midrule
	ft06 &   55 &   63 &  0.99 &&  102 &   95 &&   64 &   63 &&   66 &   63 \\
	ft10 &  930 & 1068 &   0.9 && 2183 & 1931 && 1507 & 1436 && 1464 & 1415 \\
	     &      &      &  0.99 && 2139 & 1931 && 1444 & 1353 && 1413 & 1349 \\
	     &      &      & 0.999 && 2366 & 2028 && 1380 & 1281 && 1371 & 1292 \\
	ft20 & 1165 &      &   0.9 && 2476 & 2406 && 1957 & 1866 && 1935 & 1869 \\
	     &      &      &  0.99 && 2454 & 2348 && 1840 & 1814 && 1860 & 1840 \\
	     &      &      & 0.999 && 5 & 1170 && 1165 &  130 &&   & \\[2ex]
	c1   &   34 &      &  0.99 &&   66 &   62 &&   37 &   37 &&   37 &   37 \\
	c2   &   53 &      &  0.99 &&   88 &   75 &&   65 &   65 &&   65 &   65 \\
	c3   &  143 &      &  0.99 &&  206 &  206 &&  180 &  180 &&  180 &  180 \\
	c4   &   57 &      &  0.99 &&  116 &  109 &&   94 &   92 &&   91 &   90 \\
	c5   &  113 &      &  0.99 &&  247 &  215 &&  180 &  170 &&  175 &  170 \\
	c6   &  225 &      &  0.99 &&  502 &  434 &&  365 &  360 &&  360 &  353 \\
	c7   &   39 &      &  0.99 &&   39 &   39 &&   39 &   39 &&   39 &   39 \\
	c8   &   64 &      &  0.99 &&   64 &   64 &&   64 &   64 &&   64 &   64 \\
	c9   &  138 &      &  0.99 &&  138 &  138 &&  138 &  138 &&  138 &  138 \\
	c10  &   50 &      &  0.99 &&   50 &   50 &&   50 &   50 &&   50 &   50 \\
	c11  &  103 &      &  0.99 &&  170 &  116 &&  106 &  106 &&  106 &  106 \\
	c12  &  204 &      &  0.99 &&  265 &  210 &&  208 &  208 &&  208 &  208 \\
	c13  &  337 &      &  0.99 &&  557 &  524 &&  467 &  458 &&  393 &  389 \\
	c14  &  705 &      &  0.99 && 1203 & 1036 &&  866 &  833 &&  797 &  788 \\
	c15  & 1458 &      &  0.99 && 2556 & 2258 && 1789 & 1666 && 1508 & 1493 \\
	c16  &  405 &      &  0.99 &&  519 &  483 &&  444 &  429 &&  405 &  405 \\
	c17  &  955 &      &  0.99 && 1257 & 1009 &&  962 &  955 &&  955 &  955 \\
	c18  & 1621 &      &  0.99 && 2314 & 2131 && 1710 & 1688 && 1621 & 1621 \\
	c19  & 2631 &      &  0.99 && 4568 & 3973 && 4365 & 4049 && 2631 & 2631 \\[2ex]
	v20  &      &      &   0.9 &&  571 &  540 &&  494 &  476 &&  438 &  423 \\
	     &      &      &  0.99 &&  527 &  517 &&  447 &  421 &&  424 &  418 \\
	v21  &      &      &   0.9 &&  331 &  293 &&  277 &  254 &&  218 &  215 \\
	     &      &      &  0.99 &&  327 &  291 &&  213 &  209 &&  198 &  194 \\
	v22  &      &      &   0.9 &&  419 &  387 &&  326 &  314 &&  294 &  284 \\
	     &      &      &  0.99 &&  393 &  369 &&  293 &  281 &&  273 &  262 \\
	v30  & 2381 &      &   0.9 && 4210 & 4068 && 5969 & 5856 && 3546 & 3438 \\
	     &      &      &  0.99 && 4200 & 4154 && 5591 & 5411 && 3287 & 3147 \\
	v31  &  959 &      &   0.9 && 1658 & 1573 && 4303 & 4133 && 1702 & 1635 \\
	     &      &      &  0.99 && 1688 & 1632 && 3772 & 3712 && 1646 & 1617 \\
	v32  & 1111 &      &   0.9 && 5 & 1119 && 1116 &   11 &&   & \\
	     &      &      &  0.99 && 2629 & 2601 && 1111 &  116 &&   & \\
	\bottomrule
\end{tabular}
\caption{Computational results for the FBJS}
\label{table:fbjs}
\end{table}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{booktabs}

@@

%\begin{abstract}

%This paper explores the efficacy of the critical path neighborhood for the Flexible Job Shop problem, and the Flexible Blocking Job Shop problem. A disjunctive graph representation is chosen, in combination with simulated annealing, a popular local search variant. The neighborhood is assessed based on solution quality and rate of convergence.

%\end{abstract}

@@

\subsubsection{Feasibility}

@@

\begin{figure}[h]
\centering
\begin{ganttchart}[
		x unit=0.7cm,
		y unit chart=0.7cm,
		canvas/.style={draw=none, fill=none},
		vgrid,
		vgrid={*1{draw=black!12}},
		inline,
		group/.style={draw=none, fill=none},
		bar top shift=0.1,
		bar height=0.8,
		y unit title=0.5cm,
		title/.style={draw=none, fill=none},
		include title in canvas=false,
	]{655}{669}

@@

The rest of the instances were generated using a random instance generator built for this purpose. These are labeled \emph{v20 -- v33}. The optimal makespans for these instances is unknown. However, they do provide insight into the convergence behavior, especially when compared between instances.

The local search was implemented in C, using the GCC compiler with the -O3 flag. Each configuration was run five times, to generate an average best makespan and execution time. These results can be examined in \textbf{Table \ref{table:fjs}}.

\begin{table}
\centering
\footnotesize
\begin{tabular}{@{\bfseries}rrrrrrrrrrrr}
	\toprule
	\multicolumn{4}{c}{Instance} & \multicolumn{2}{c}{Properties} && \multicolumn{5}{c}{Results} \\
	\cmidrule(r){1-4} \cmidrule(lr){5-6} \cmidrule(lr){8-12}
	\normalfont{name} & $|\mathcal{J}|$ & $|\mathcal{T}|$ & $|\mathcal{M}|$ & $\max C_\text{job}$ &
	$C_\text{opt}$ && $\alpha$ & restarts & $\bar{C}$ & $C_\text{best}$ & $\bar{t}$ \\
	\midrule
	ft06 &  6 &  6 &  6 &   47 &   55 &&    0.9 & 1 &   55 &   55 &    0 \\
	ft10 & 10 & 10 & 10 &  655 &  930 &&    0.9 & 5 &  954 &  941 &    2 \\
	     &    &    &    &      &      &&   0.99 & 5 &  943 &  938 &   18 \\
	     &    &    &    &      &      &&  0.999 & 5 &  933 &  930 &  182 \\
	ft20 & 20 &  5 &  5 &  387 & 1165 &&    0.9 & 5 & 1215 & 1186 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 & 1182 & 1178 &   13 \\
	     &    &    &    &      &      &&  0.999 & 5 & 1170 & 1165 &  130 \\[2ex]
	c1   &  4 &  2 &  4 &   34 &   34 &&    0.9 & 1 &   34 &   34 &    0 \\
	c2   &  4 &  2 &  4 &   53 &   53 &&    0.9 & 1 &   53 &   53 &    0 \\
	c3   &  4 &  2 &  4 &  133 &  143 &&    0.9 & 1 &  143 &  143 &    0 \\
	c4   &  6 &  2 &  4 &   52 &   57 &&   0.99 & 5 &   57 &   57 &    2 \\
	c5   &  6 &  2 &  4 &  105 &  113 &&   0.99 & 5 &  113 &  113 &    2 \\
	c6   &  6 &  2 &  4 &  205 &  225 &&   0.99 & 5 &  225 &  225 &    2 \\
	c7   &  4 &  3 &  9 &   39 &   39 &&    0.9 & 1 &   39 &   39 &    0 \\
	c8   &  4 &  3 &  9 &   64 &   64 &&    0.9 & 1 &   64 &   64 &    0 \\
	c9   &  4 &  3 &  9 &  138 &  138 &&    0.9 & 1 &  138 &  138 &    0 \\
	c10  &  6 &  3 &  9 &   50 &   50 &&    0.9 & 1 &   50 &   50 &    0 \\
	c11  &  6 &  3 &  9 &  103 &  103 &&    0.9 & 1 &  103 &  103 &    0 \\
	c12  &  6 &  3 &  9 &  204 &  204 &&    0.9 & 1 &  204 &  204 &    0 \\
	c13  &  8 &  3 &  9 &  337 &  337 &&    0.9 & 5 &  337 &  337 &    0 \\
	c14  &  8 &  3 &  9 &  705 &  705 &&    0.9 & 5 &  705 &  705 &    0 \\
	c15  &  8 &  3 &  9 & 1458 & 1458 &&    0.9 & 5 & 1458 & 1458 &    0 \\
	c16  & 10 &  4 & 16 &  405 &  405 &&    0.9 & 5 &  405 &  405 &    0 \\
	c17  & 10 &  4 & 16 &  955 &  955 &&    0.9 & 5 &  955 &  955 &    0 \\
	c18  & 10 &  4 & 16 & 1621 & 1621 &&    0.9 & 5 & 1621 & 1621 &    0 \\
	c19  & 15 &  5 & 25 & 2631 & 2631 &&    0.9 & 5 & 2631 & 2631 &    0 \\[2ex]
	v20  &  8 &  2 &  4 &  176 &      &&    0.9 & 5 &  387 &  387 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 &  387 &  387 &    7 \\
	     &    &    &    &      &      &&  0.999 & 5 &  387 &  387 &   67 \\
	v21  &  8 &  2 &  8 &  187 &  187 &&    0.9 & 5 &  204 &  188 &    0 \\
	     &    &    &    &      &      &&   0.99 & 5 &  197 &  188 &    4 \\
	     &    &    &    &      &      &&  0.999 & 5 &  188 &  187 &   25 \\
	v22  &  8 &  4 &  8 &  195 &      &&    0.9 & 5 &  237 &  237 &    1 \\
	     &    &    &    &      &      &&   0.99 & 5 &  237 &  237 &    9 \\
	     &    &    &    &      &      &&  0.999 & 5 &  237 &  237 &   82 \\
	v30  & 16 &  2 &  4 &  666 &      &&    0.9 & 5 & 2382 & 2381 &   10 \\
	     &    &    &    &      &      &&   0.99 & 5 & 2381 & 2381 &  102 \\
	     &    &    &    &      &      &&  0.999 & 5 & 2381 & 2381 & 1045 \\
	v31  & 16 &  2 &  8 &  566 &      &&    0.9 & 5 &  963 &  961 &   12 \\
	     &    &    &    &      &      &&   0.99 & 5 &  960 &  959 &  126 \\
	     &    &    &    &      &      &&  0.999 & 5 &  958 &  956 & 1238 \\
	v32  & 16 &  4 &  8 &  655 &      &&    0.9 & 5 & 1119 & 1116 &   11 \\
	     &    &    &    &      &      &&   0.99 & 5 & 1112 & 1111 &  116 \\
	     &    &    &    &      &      &&  0.999 & 5 & 1108 & 1106 & 1164 \\
	v33  & 16 &  4 & 16 &  626 &  626 &&    0.9 & 5 &  628 &  626 &    5 \\
	     &    &    &    &      &      &&   0.99 & 5 &  657 &  651 &   84 \\
	\bottomrule
\end{tabular}
\caption{Computational results for the FJS}
\label{table:fjs}
\end{table}

Most of the parameters in the table are self-explanatory. The times are given in seconds, for an Intel Core i3 M370 @ 2.40 Hz CPU. $\alpha$ is the cooling parameter. It is responsible for lowering the tempterature of the simulated annealing process. A value closer to 1 means the temperature cools more slowly, and thus the heuristic searches longer. The restarts column indicates how many times the temperature was reset. The average best makespans are indicated by $\bar{C}$, and the average running times by $\bar{t}$.

@@

For the Job Shop instances (\emph{ft06}, \emph{ft10}, and \emph{ft20}), the code performs as well as previous results in literature \cite{simulatedannealingjsp}. This gives us confidence that the code is robust.

The series of instances from the previous project (\emph{c1 -- c19}) are largely uninteresting, due to there being too few jobs in relation to machines. For the few instances whose optimal makespans were larger than the lower bound given by the job makespans, the search had significantly more trouble finding the optimum, despite being much smaller than some of the other instances. In several cases, the search failed to find an optimal solution despite the restarts, being very slightly off. However, this was averaged out by the other results. It should be noted that in some of these cases, the algorithm actually became stuck in a small area of the solution space, with the only neighborhood solution available being infeasible. This is very rare, but it highlights the importance of random restarts when using the critical path neighborhood for the FJS.

@@

The Flexible Blocking Job Shop adds the blocking constraint to the problem. This constraint adds a new degree of complexity to the problem, and is notoriously difficult to solve. Any optimal makespan found will be at least as large as its non-blocking counterpart. Completing jobs in the shortest timespan possible suddenly becomes very important, in order to reduce the total time a machine spends being blocked.

@@

The same instances are used as before. The restarts were held constant at five. A new column, containing the best non-blocking solution for the instance, is added for comparison. The results can be explored in \textbf{Table \ref{table:fbjs}}.

No running times are listed, but in general they are in the same order as for the FJS (a bit more, the blocking constraints do add some extra computation).

\begin{table}
\centering
\footnotesize
\begin{tabular}{@{\bfseries}rrrrrrrrrrrrr}
	\toprule
	& FJS & FBJS & && \multicolumn{2}{c}{Critical Path} &&
	\multicolumn{2}{c}{Naive shift} && \multicolumn{2}{c}{Both} \\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){6-7}
	\cmidrule(lr){9-10} \cmidrule(lr){12-13}
	\normalfont{name} & $C_\text{best}$ & $C_\text{opt}$ & $\alpha$ && $\bar{C}$ & $C_\text{best}$ &&
	$\bar{C}$ & $C_\text{best}$ && $\bar{C}$ & $C_\text{best}$ \\
	\midrule
	ft06 &   55 &   63 &  0.99 &&  102 &   95 &&   64 &   63 &&   66 &   63 \\
	ft10 &  930 & 1068 &   0.9 && 2183 & 1931 && 1507 & 1436 && 1464 & 1415 \\
	     &      &      &  0.99 && 2139 & 1931 && 1444 & 1353 && 1413 & 1349 \\
	     &      &      & 0.999 && 2366 & 2028 && 1380 & 1281 && 1371 & 1292 \\
	ft20 & 1165 &      &   0.9 && 2476 & 2406 && 1957 & 1866 && 1935 & 1869 \\
	     &      &      &  0.99 && 2454 & 2348 && 1840 & 1814 && 1860 & 1840 \\
	     &      &      & 0.999 && 2393 & 2209 && 1694 & 1646 && 1714 & 1632 \\[2ex]
	c1   &   34 &      &  0.99 &&   66 &   62 &&   37 &   37 &&   37 &   37 \\
	c2   &   53 &      &  0.99 &&   88 &   75 &&   65 &   65 &&   65 &   65 \\
	c3   &  143 &      &  0.99 &&  206 &  206 &&  180 &  180 &&  180 &  180 \\
	c4   &   57 &      &  0.99 &&  116 &  109 &&   94 &   92 &&   91 &   90 \\
	c5   &  113 &      &  0.99 &&  247 &  215 &&  180 &  170 &&  175 &  170 \\
	c6   &  225 &      &  0.99 &&  502 &  434 &&  365 &  360 &&  360 &  353 \\
	c7   &   39 &   39 &  0.99 &&   39 &   39 &&   39 &   39 &&   39 &   39 \\
	c8   &   64 &   64 &  0.99 &&   64 &   64 &&   64 &   64 &&   64 &   64 \\
	c9   &  138 &  138 &  0.99 &&  138 &  138 &&  138 &  138 &&  138 &  138 \\
	c10  &   50 &   50 &  0.99 &&   50 &   50 &&   50 &   50 &&   50 &   50 \\
	c11  &  103 &      &  0.99 &&  170 &  116 &&  106 &  106 &&  106 &  106 \\
	c12  &  204 &      &  0.99 &&  265 &  210 &&  208 &  208 &&  208 &  208 \\
	c13  &  337 &      &  0.99 &&  557 &  524 &&  467 &  458 &&  393 &  389 \\
	c14  &  705 &      &  0.99 && 1203 & 1036 &&  866 &  833 &&  797 &  788 \\
	c15  & 1458 &      &  0.99 && 2556 & 2258 && 1789 & 1666 && 1508 & 1493 \\
	c16  &  405 &  405 &  0.99 &&  519 &  483 &&  444 &  429 &&  405 &  405 \\
	c17  &  955 &  955 &  0.99 && 1257 & 1009 &&  962 &  955 &&  955 &  955 \\
	c18  & 1621 & 1621 &  0.99 && 2314 & 2131 && 1710 & 1688 && 1621 & 1621 \\
	c19  & 2631 & 2631 &  0.99 && 4568 & 3973 && 4365 & 4049 && 2631 & 2631 \\[2ex]
	v20  &  387 &      &   0.9 &&  571 &  540 &&  494 &  476 &&  438 &  423 \\
	     &      &      &  0.99 &&  527 &  517 &&  447 &  421 &&  424 &  418 \\
	v21  &  187 &      &   0.9 &&  331 &  293 &&  277 &  254 &&  218 &  215 \\
	     &      &      &  0.99 &&  327 &  291 &&  213 &  209 &&  198 &  194 \\
	v22  &  237 &      &   0.9 &&  419 &  387 &&  326 &  314 &&  294 &  284 \\
	     &      &      &  0.99 &&  393 &  369 &&  293 &  281 &&  273 &  262 \\
	v30  & 2381 &      &   0.9 && 4210 & 4068 && 5969 & 5856 && 3546 & 3438 \\
	     &      &      &  0.99 && 4200 & 4154 && 5591 & 5411 && 3287 & 3147 \\
	v31  &  959 &      &   0.9 && 1658 & 1573 && 4303 & 4133 && 1702 & 1635 \\
	     &      &      &  0.99 && 1688 & 1632 && 3772 & 3712 && 1646 & 1617 \\
	v32  & 1111 &      &   0.9 && 2570 & 2389 && 5214 & 5054 && 2570 & 2389 \\
	     &      &      &  0.99 && 2629 & 2601 && 4481 & 4209 && 2171 & 1983 \\
	v33  &  626 &      &   0.9 && 1296 & 1212 && 3182 & 2931 && 1098 & 1053 \\
	     &      &      &  0.99 && 1335 & 1244 && 2061 & 1903 &&  952 &  894 \\
	\bottomrule
\end{tabular}
\caption{Computational results for the FBJS}
\label{table:fbjs}
\end{table}
